Combining global tree cover loss data with historical national forest-cover maps to look at six decades of deforestation and forest fragmentation in Madagascar

### 2017-06-19 report/deforestmap.tex
Submission to Biological Conservation

\documentclass[a4paper, 12pt, leqno]{article} %leqno: numéro d'équation à gauche
\pagenumbering{arabic} % choose how to number the pages
\usepackage{a4wide}
\usepackage[utf8]{inputenc} % accents interprétés
\usepackage{graphicx}
%\usepackage{subfig}
%\usepackage[hmargin=2cm, vmargin = 2cm, noheadfoot]{geometry} %% Pour gérer le format des pages
%\usepackage{layout} %% Pour avoir la longueur des marges
\usepackage[round,sort]{natbib} %% Natbib is a popular style for formatting references.
%\usepackage{multibib}
%\newcites{secnm}{Bibliographie} 
%\usepackage{verbatim} % for multiline comments
\usepackage{amssymb} %symbole de maths
\usepackage{amsmath} %idem
%\usepackage{stmaryrd} %% Symbole flèche à l'envers
%\usepackage{amsfonts}
\usepackage[english]{babel} %% Les titres en anglais
\usepackage{array} %% Pour centrer verticalement le contenu d'un tableau, entre autres...
\setcounter{secnumdepth}{4} %% Profondeur des sections, subsections
\usepackage{setspace} %% Gère l'interligne: singlespacing, doublespacing
\usepackage{booktabs}
%\singlespacing
\usepackage{longtable}
\setlength{\LTleft}{-5cm plus 1 fill}
\setlength{\LTright}{-5cm plus 1 fill}
\usepackage[colorlinks=true,citecolor=blue]{hyperref} %% Gère les hyperliens
\usepackage{lineno} %% Numérotation des lignes
\usepackage{caption}
%\linenumbers
\newcommand{\logit}{\text{logit}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\p}{\text{p}}
\newcommand{\R}{\textnormal{\sffamily\bfseries R}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

@@

\begin{center}
  \textbf{Running headline:} \emph{Six decades of deforestation in Madagascar}
\end{center}

@@

\linenumbers
\doublespacing

@@

  1. The island of Madagascar has an unparalleled biodiversity, mainly
  located in the tropical forests of the island, which is highly
  threatened by anthropogenic deforestation. Scattered forest maps
  from past studies at national level with substantial gaps (due to
  presence of cloud cover on satellite imagery) prevent the analyzis
  of long-term deforestation trends in Madagascar.

  2. In this study, we propose a new approach combining historical
  (1953-2000) national forest-cover maps with recent (2001-2014)
  global annual tree cover loss data to look at six decades
  (1953-2014) of deforestation and forest fragmentation in
  Madagascar. We produced new forest-cover maps at 30~m resolution over
  the full territory of Madagascar for the year 1990, and annually
  from 2000 to 2014.

  3. We estimated that Madagascar has lost 44\% of its natural forest
  cover over the period 1953-2014 (including 37\% over the period
  1973-2014). Natural forests cover 8.9 Mha in 2014 (15\% of the
  national territory) which are divided into 4.4 Mha (50\%) of moist
  forests, 2.6 Mha (29\%) of dry forests, 1.7 Mha of spiny forests
  (19\%) and 177,000 ha (2\%) of mangroves. Since 2005, the annual
  deforestation rate has progressively increased in Madagascar to
  reach 99,000 ha/yr during 2010-2014 (corresponding to a rate of
  1.08\%/yr). This increase is probably due to rapid population growth
  (close to 3\%/yr) and to poor law enforcement in the country. Around
  half of the forest (46\%) is now located at less than 100m from the
  forest edge.

  4. \emph{Policy implications}: Accurate forest-cover change maps can
  be used to assess the effectiveness of past and current conservation
  programs and implement new strategies for the future. In particular,
  forest maps and estimates can be used in the framework of the REDD+
  (``Reducing Emissions from Deforestation and Forest Degradation'')
  initiative and for optimizing the current protected area network.

@@

\keywords{biodiversity, climate-change, deforestation, Madagascar, tropical forest}

@@

    \includegraphics[width=11cm]{outputs/ecoregion.png}

@@

  \includegraphics[width=\textwidth]{outputs/fig_fcc_highres.png}

@@

  \includegraphics[width=13cm]{outputs/dist.png}

>>>>

\documentclass[a4paper, 12pt, leqno]{article} %leqno: numéro d'équation à gauche
\pagenumbering{arabic} % choose how to number the pages
\usepackage{a4wide}
\usepackage[utf8]{inputenc} % accents interprétés
\usepackage{graphicx}
%\usepackage{subfig}
%\usepackage[hmargin=2cm, vmargin = 2cm, noheadfoot]{geometry} %% Pour gérer le format des pages
%\usepackage{layout} %% Pour avoir la longueur des marges
\usepackage[round,sort]{natbib} %% Natbib is a popular style for formatting references.
%\usepackage{multibib}
%\newcites{secnm}{Bibliographie} 
%\usepackage{verbatim} % for multiline comments
\usepackage{amssymb} %symbole de maths
\usepackage{amsmath} %idem
%\usepackage{stmaryrd} %% Symbole flèche à l'envers
%\usepackage{amsfonts}
\usepackage[english]{babel} %% Les titres en anglais
\usepackage{array} %% Pour centrer verticalement le contenu d'un tableau, entre autres...
\setcounter{secnumdepth}{4} %% Profondeur des sections, subsections
\usepackage{setspace} %% Gère l'interligne: singlespacing, doublespacing
\usepackage{booktabs}
%\singlespacing
\usepackage{longtable}
\setlength{\LTleft}{-5cm plus 1 fill}
\setlength{\LTright}{-5cm plus 1 fill}
\usepackage[colorlinks=true,citecolor=blue]{hyperref} %% Gère les hyperliens
\usepackage{lineno} %% Numérotation des lignes
%\linenumbers
\usepackage{caption2}
\newcommand{\logit}{\text{logit}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\p}{\text{p}}
\newcommand{\R}{\textnormal{\sffamily\bfseries R}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

@@

{\small
   \begin{flushleft}
   \textbf{Highlights:}\\
    -We produced new 30 m resolution annual forest-cover maps for Madagascar for the period 2000-2014.\\
   - Madagascar has lost 44\% of its natural forest-cover over the period 1953-2014.\\
   - Half of the tropical forest in Madagascar is now located at less than 100m from forest edge.\\
   - Annual deforestation rate has increased in Madagascar since 2005 to reach 1.08\%/yr.\\
   - Conservation efforts must be intensified to save Madagascar unique forests and biodiversity.\\
\end{flushleft}}

@@

\doublespacing
\linenumbers

@@

  The island of Madagascar has an unparalleled biodiversity, mainly
  located in the tropical forests of the island, which is highly
  threatened by anthropogenic deforestation. Scattered forest maps
  from past studies at national level with substantial gaps (due to
  presence of cloud cover on satellite imagery) prevent the analysis
  of long-term deforestation trends in Madagascar. In this study, we propose 
  a new approach combining historical
  (1953-2000) national forest-cover maps with recent (2001-2014)
  global annual tree cover loss data to look at six decades
  (1953-2014) of deforestation and forest fragmentation in
  Madagascar. We produced new forest-cover maps at 30~m resolution over
  the full territory of Madagascar for the year 1990, and annually
  from 2000 to 2014. We estimated that Madagascar has lost 44\% of its natural forest
  cover over the period 1953-2014 (including 37\% over the period
  1973-2014). Natural forests cover 8.9 Mha in 2014 (15\% of the
  national territory) which are divided into 4.4 Mha (50\%) of moist
  forests, 2.6 Mha (29\%) of dry forests, 1.7 Mha of spiny forests
  (19\%) and 177,000 ha (2\%) of mangroves. Since 2005, the annual
  deforestation rate has progressively increased in Madagascar to
  reach 99,000 ha/yr during 2010-2014 (corresponding to a rate of
  1.08\%/yr). This increase is probably due to rapid population growth
  (close to 3\%/yr) and to poor law enforcement in the country. Around
  half of the forest (46\%) is now located at less than 100m from the
  forest edge. Accurate forest-cover change maps can
  be used to assess the effectiveness of past and current conservation
  programs and implement new strategies for the future. In particular,
  forest maps and estimates can be used in the framework of the REDD+
  (``Reducing Emissions from Deforestation and Forest Degradation'')
  initiative and for optimizing the current protected area network.

@@

\keywords{biodiversity, climate-change, deforestation, forest-fragmentation, Madagascar, tropical forest}

@@

    \includegraphics[width=11cm]{ecoregion.png}

@@

  \includegraphics[width=\textwidth]{fig_fcc_highres.png}

@@

  \includegraphics[width=13cm]{dist.png}
